Stats

### 2023-06-05 stats/analysis.Rmd
adjust lifespan plot

```{r lifespan_plot}
ggplot(data = lifespan_variation, aes(x = age, y = mean)) +
  geom_point(color = "darkgrey", alpha = 0.5) +
  geom_smooth(method = "loess", size = 1, se = F, color = "#006c66") + 
  scale_x_continuous(limits = c(0, 80), breaks = seq(0, 80, 5)) + 
  scale_y_continuous(limits = c(0, 4), breaks = seq(0, 4, 0.5)) + 
  labs(x = "Age in years", y = "Average imprecision in target widths")

>>>>

```{r lifespan_plot}
ggplot(data = lifespan_variation, aes(x = age, y = mean)) +
  geom_point(color = "darkgrey", alpha = 0.5) +
  geom_smooth(method = "loess", size = 1, se = T, color = "#006c66", fill = "#006c66") + 
  scale_x_continuous(limits = c(0, 80), breaks = seq(0, 80, 5)) + 
  scale_y_continuous(limits = c(0, 4), breaks = seq(0, 4, 0.5)) + 
  labs(x = "Age in years", y = "Average imprecision in target widths")
